What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-29 paper/main.tex
replace href with words

%KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
%\paragraph{Real-world datasets}
{\bf Feasibility.}
We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
%
We gather a test suite totalling 91 formulas from two real-world requirement specification applications. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas from the suite of $23$ collections of formulas were collected. We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas. The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/blob/main/ltl-formulas/benchmark-ltls.txt}{here}.

@@

%\paragraph{Scalability}
{\bf Scalability.}
We study the scalability of our tool on a benchmark suite of LTL formulas that scales in size. According to Rozier and Vardi~\cite{RV10}, the LTL formula required to encode a $n$-bit binary counter scales in size as $n$ gets larger. Therefore the benchmark for scalability consists of LTL formulas that describe $n$-bit counters. \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}. The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas/binary_counter}{here}.

@@

\section{Artifact Availability: ``Thought is free\textsuperscript{\textsection}'' }
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{The Tempest}}
\endgroup
The tool we present in this paper is available at
\[
    \texttt{\url{https://github.com/EULIR/ltl-explainability}}
\]
which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.

The set of LTL formulas we used to evaluate our tool in \cref{sec:playing} can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas}{here}.

>>>>

%KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
%\paragraph{Real-world datasets}
{\bf Feasibility.}
We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
%
We gather a test suite totalling 91 formulas from two real-world requirement specification applications. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas from the suite of $23$ collections of formulas were collected. We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.

@@

%\paragraph{Scalability}
{\bf Scalability.}
We study the scalability of our tool on a benchmark suite of LTL formulas that scales in size. According to Rozier and Vardi~\cite{RV10}, the LTL formula required to encode a $n$-bit binary counter scales in size as $n$ gets larger. Therefore the benchmark for scalability consists of LTL formulas that describe $n$-bit counters. \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.

@@

\section{Artifact Availability: ``Thought is free\textsuperscript{\textsection}'' }
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{The Tempest}}
\endgroup
The tool we present in this paper is available at
\[
    \texttt{\url{https://github.com/EULIR/ltl-explainability}}
\]
which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found in the artifact repository.

The set of LTL formulas we used to evaluate our tool in \cref{sec:playing} can be found in the artifact repository under \texttt{ltl-formulas} directory.
